Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-12 paper/paper.tex
pass on section 7 (Hermes)

\section{Discussion}
\label{sec:bugs}

\subsection{Example Bug Reports}

>>>>

\section{Case Study: \hermes}
\label{sec:bugs}

This section describes the experiment we conducted to evaluate the
effectiveness of the techniques we studied to find new bugs in
\hermes, a JavaScript engine that has started development very
recently. \hermes is a JavaScript engine introduced by Facebook in
2019. According to its website, \hermes is ``a JavaScript engine
optimized for fast start-up of React Native apps on
Android''~\cite{hermes2020repo}.\Mar{short sentence saying where it is
  used.}

%  for performing 
As a preparatory step to apply test transplantation and differential
testing to \hermes, we ran the Test262 conformance suite on the most
recent version of \hermes, 0.5.0. We observed that only 26\% of the
Test262 tests passed. When taking a closer look, we noticed that this
high percentage of failing tests was due to the high number of
features not yet suported by \hermes\footnote{See
  \url{https://github.com/facebook/hermes/blob/master/doc/Features.md}}. For
instance, in its most recent release, \hermes still does not support
for features such as Proxy, Promise, and Async calls. For this
reason---low coverage on Test262---, we opted not to include \hermes
with other JavaScript engines. Since we only fuzz test files that pass
in all engines, this would require us to significantly reduce the
number of tests used in the experiments, affecting overall results.

We followed the same methodology described in previous sections to
evaluate \hermes. When experimenting with test transplantation, we
noted many errors when replaying the test suite of \smonkey on
\hermes. This happened because \smonkey has its own assertion
framework, but \hermes was unable to interpret those assertions,
resulting in failures in all test executions from this engine. These
failures did not happen when the \smonkey tests were transplanted to
the other engines, though\Mar{Why? Was the framework using some of the
  features aforementioned? Say it, please.}. Overall, we repoted three
issues to the \hermes bug tracker as result of using test
transplantation\footnote{\url{https://github.com/facebook/hermes/issues/<id>},
  with id 265, 266, 267.}. One of them was confirmed by the \hermes
maintainers by the time of this submission. For another, the
maintainer explained the issue was related to a feature not yet
supported---a \texttt{return} statement outside the scope of a
block. For the third issue, developers disagreed on the proper
implementation of one particular part of the specification involved in
the issue (i.e., whether a numeric escape character (non-octal-eight,
\texttt{\textbackslash{8}}) should be allowed or not in strict
mode. The issue was closed, but the maintainers opened a new one to
discuss this matter. By following the discussion, it was interesting
to observe that maintainers are aware that this feature is implemented
by other engines such as \veight, \chakra, and \smonkey. Yet, they
were unsure how they should treat it in \hermes.  Considering
differential testing, we found and reported one bug on \hermes using
\radamsa. As of this writing, this particular bug report was not yet
addressed by any \hermes maintainer.

Overall, we noted that test transplantation and differential testing
were effective techniques in revealing potential bugs in non-trivial
JavaScript engines of varying degrees of maturity. We found bugs both
in extremely robust and largely adopted engines and also in recently
developed engines. \Mar{check $\rightarrow$}The issue diagnosis of
developers seem to differ though. Issues reported to stable engines
are more likely to be real bugs---as lots of problems have been
already scrutinized---whereas issues reported to new engines are more
likely to be inconsistencies related to influx development as opposed
to real bugs.

\section{Discussion}

This section discusses bug reports, threats to validity, and key
findings and lessons learned.

\subsection{Bug Reports}
